\bf Model Visualization Techniques for a Social Network Model

### 2017-04-13 paper.Rnw
just color nodes in ex data

<<alldataviz, fig.cap="The smaller friendship network data we will be modelling throughout the paper.", fig.width=8>>=
actual1 <- merge(data.frame(as.edgelist(as.network(fd2.w1))), 
                 data.frame(id = 1:16, drink = drink2[,1]),
                 by.x = "X1", by.y = "id", all = T)
actual1$Wave <- 1 
actual2 <- merge(data.frame(as.edgelist(as.network(fd2.w2))),
                 data.frame(id = 1:16,drink = drink2[,2]),
                 by.x = "X1", by.y = "id", all = T)
actual2$Wave <- 2
actual3 <- merge(data.frame(as.edgelist(as.network(fd2.w3))),
                 data.frame(id = 1:16,drink = drink2[,3]),
                 by.x = "X1", by.y = "id", all = T)
actual3$Wave <- 3
alldat <- rbind(actual1, actual2, actual3)
alldat$X1 <- paste0("V", alldat$X1)
alldat$X2 <- ifelse(!is.na(alldat$X2), paste0("V", alldat$X2), NA)
alldataviz <- ggplot(data = alldat, 
       aes(from_id = X1, to_id = X2, color = as.ordered(drink), group = as.ordered(drink))) +
  geom_net(fiteach = FALSE, directed=TRUE, layout.alg = 'fruchtermanreingold', size = 3, arrowsize = .5, arrowgap = .03) +
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  theme_net() +
  facet_wrap(~Wave, labeller = "label_both") + 
  theme(legend.position = 'bottom', panel.background = element_rect(fill = NA, color = "grey30"))
alldataviz
@

>>>>

<<alldataviz, fig.cap="The smaller friendship network data we will be modelling throughout the paper.", fig.width=8>>=
actual1 <- merge(data.frame(as.edgelist(as.network(fd2.w1))), 
                 data.frame(id = 1:16, drink = drink2[,1]),
                 by.x = "X1", by.y = "id", all = T)
actual1$Wave <- 1 
actual2 <- merge(data.frame(as.edgelist(as.network(fd2.w2))),
                 data.frame(id = 1:16,drink = drink2[,2]),
                 by.x = "X1", by.y = "id", all = T)
actual2$Wave <- 2
actual3 <- merge(data.frame(as.edgelist(as.network(fd2.w3))),
                 data.frame(id = 1:16,drink = drink2[,3]),
                 by.x = "X1", by.y = "id", all = T)
actual3$Wave <- 3
alldat <- rbind(actual1, actual2, actual3)
alldat$X1 <- paste0("V", alldat$X1)
alldat$X2 <- ifelse(!is.na(alldat$X2), paste0("V", alldat$X2), NA)
alldataviz <- ggplot(data = alldat, 
       aes(from_id = X1, to_id = X2, color = as.ordered(drink), group = as.ordered(drink))) +
  geom_net(fiteach = FALSE, directed=TRUE, layout.alg = 'fruchtermanreingold', size = 3, arrowsize = .5, arrowgap = .03, ecolor = 'grey40') +
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  theme_net() +
  facet_wrap(~Wave, labeller = "label_both") + 
  theme(legend.position = 'bottom', panel.background = element_rect(fill = NA, color = "grey30"))
alldataviz
@
